### 2018-03-27 latex/sc18/prelims.tex

When applying the BCD method to a constrained non-linear programming
problem, we have to ensure the following (a) it is critical to wisely choose a partition of
$\mathcal{X}$, whose Cartesian product constitutes $\mathcal{X}$. 
(b)  the dependency among the subproblems -- independent blocks can be 
computed simultaneously  (c) when updating a block, ensure we are 
using the most recent other blocks and (d) importantly, every block
must be solved optimally. Every NTF variant will have different the partition
scheme for blocks with natural partition such as scalar, vector \cite{CP2009} and matrix \cite{KP2011}. 
Also, the update equation for determining the optimal block given
other blocks such as projected gradient, block principal pivoting \cite{KP2011}  etc. 
A detailed discussion of equivalences and comparison of different NMF and NTF algorithm
is presented at \cite{KHP2014}.

@@

Our paper can be extended to other NTF algorithms such as AO-ADMM \cite{HSL2015} and Nestrov based updates
\cite{LKLHS2017} by changing the $Local-NLS-Update$ function of the proposed Algorithm \ref{alg:2D}.

>>>>

When applying the BCD method to a constrained non-linear programming
problem, we have to ensure the following (a) it is critical to wisely choose a partition of
$\mathcal{X}$, whose Cartesian product constitutes $\mathcal{X}$. 
(b)  the dependency among the subproblems -- independent blocks can be 
computed simultaneously  (c) when updating a block, ensure we are 
using the most recent other blocks and (d) importantly, every block
must be solved optimally. Every NTF variant will have different the partition
scheme for blocks with natural partition such as scalar \cite{SL2001}, vector \cite{CP2009} and matrix \cite{KP2011}. 
Also, the update equation for determining the optimal block given
other blocks such as projected gradient, block principal pivoting \cite{KP2011}  etc. 
A detailed discussion of equivalences and comparison of different NMF and NTF algorithm
is presented at \cite{KHP2014}.

@@

Our paper can be extended to other NTF algorithms such as Alternating Optimization and Alternating Direction Method of Multipliers (AO-ADMM) \cite{HSL2015, SBK2017} and Nestrov based updates
\cite{LKLHS2017} by changing the $Local-NLS-Update$ function of the proposed Algorithm \ref{alg:2D}.
